Using an overlapping domain method works well for some situations; however, there are situations that arise in which we would like to de-couple the sub-domains entirely. To motivate this method I will switch to a cell-centered approach. Starting in 1-D again we can visualize this using figure \ref{fig:4.1} which depicts a straight line with nodes at the center of each cell. We use the same central difference approximation we showed in equation \ref{eq:3.1}. The system boundaries are indicated at $u|_{x=0}$ and $u|_{x=1}$. For the non-overlapping case we define the boundary between two sub-domains as $\Gamma$. The value of $u$ on the boundary is then $\gamma$, so I have indicated the interior boundary $\Gamma$ at ${u|_{\Gamma} = \gamma}$.

\input{figures/figure_7}

We can define $\gamma$ to be the average of its neighbor nodes as shown in equation \ref{eq:4.1}.

\begin{equation}\label{eq:4.1}
	\gamma = \frac{u_{j} + u_{j+1}}{2}
\end{equation}

In figure \ref{fig:4.2} we have decomposed the domain into two sub-domains, $\Omega_0$ and $\Omega_1$. Unlike the node-centered case, the two sub-domains do not share any nodes or receive any values for ghost nodes. Instead we enforce equation \ref{eq:4.1} as a Dirichlet boundary condition between the two sub-domains. 

\pagebreak
\input{figures/figure_8}

The matrix system using the 3-point stencil before decomposition is shown below.

\input{eqsystems/sys_10}

From figure \ref{fig:4.2} we can see that on the boundary we have the following system of equations.

\input{eqsystems/sys_11}

Solving \ref{eq:4.4} for $u_0^1$ and $u_n^0$ and plugging into \ref{eq:4.2} and \ref{eq:4.3} respectively we obtain the system of equations below. These let us construct the subsequent decomposed matrix.

\input{eqsystems/sys_12}
\input{eqsystems/sys_13}

This shows that if we know the $\gamma$ values, we can completely decouple the system into smaller systems that we can solve much faster and in parallel.





